Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-01 Paper/results.tex

Similar conclusions can be drawn by examining the turbulent integral
length scale $L$.  This lengthscale can be calculated from $\langle
R_{11}(\boldsymbol{\xi}) \rangle$ via
\begin{equation}
  L = \int_0^\infty \langle R_{11}(\xi) \rangle \: {\textrm d}\xi
\end{equation}
and the results are shown in table \ref{tab:GridStudyLscale}.  With a
resolution of 2.5m, the ratio of the longitudinal length scale to the
grid size $L/\textrm{d}x \approx 10.1$, while in the lateral direction
$L/\textrm{d}x \approx 2.36$, suggesting even finer resolution is
required to capture the lateral scales.  Based on this longitudinal
length scale, we also determined the overall domain size necessary for
stable ABL calculations.  A minimum domain of 750m $\times$ 750m in
the horizontal directions was used in all Nalu-Wind and AMR-Wind LES
calculations, which provided sufficient space for the largest
turbulent structures to develop and evolve without interference from
the boundaries or other structures.

@@

%%%%%%%%%%% All stability correlation figure %%%%%%%%%%%%%%%%%%%%
% created in Postprocessing/ABLLength/CompareAll_ABL_Lengthscales.ipynb 
\begin{figure}[hbt!]
  \centering
  \fxnote{Fix legend and line styles} \\
  \includegraphics[width=3in]{figures/AllStability_Rij_Longitudinal.png}
  \includegraphics[width=3in]{figures/AllStability_Rij_Lateral.png}
  \caption{ \label{fig:AllStabilityRij} Calculation of the averaged
    longitudinal and lateral $R_{11}(\xi)$ coefficient at $z$=20m for
    all ABL stability cases.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

Similar conclusions can be drawn by examining the turbulent integral
length scale $L$.  This lengthscale can be calculated from $\langle
R_{11}(\boldsymbol{\xi}) \rangle$ via
\begin{equation}
  L = \int_0^\infty \langle R_{11}(\xi) \rangle \: {\textrm d}\xi
\end{equation}
and the results are shown in table \ref{tab:GridStudyLscale}.  With a
resolution of 2.5m, the ratio of the longitudinal length scale to the
grid size $L/\textrm{d}x \approx 10.1$, while in the lateral direction
$L/\textrm{d}x \approx 2.36$, suggesting even finer resolution is
required to capture the lateral scales.

Based on this longitudinal length scale, we also determined the
overall domain size necessary for stable ABL calculations.  To provide
sufficient space to ensure development and decorrelation of turbulent
structures, domain sizes of approximately 10 times the longitudinal
lengthscale is recommended.  However, the inclusion of sample probes
with sufficient separation distance to accurately calculate $\langle
R_{11}(\boldsymbol{\xi}) \rangle$ roughly doubles the domain size
requirements.  Assuming the longitudinal length scales on the order of
30 m, we estimated a minimum domain size of 750m $\times$ 750m in the
horizontal directions for both the Nalu-Wind and AMR-Wind LES
calculations.

@@

%%%%%%%%%%% All stability correlation figure %%%%%%%%%%%%%%%%%%%%
% created in Postprocessing/ABLLength/CompareAll_ABL_Lengthscales.ipynb 
\begin{figure}[hbt!]
  \centering
  \fxnote{Fix legend and line styles} \\
  \includegraphics[width=3in]{figures/AllStability_Rij_Longitudinal.png}
  \includegraphics[width=3in]{figures/AllStability_Rij_Lateral.png}
  \caption{ \label{fig:AllStabilityRij} Calculation of the averaged
    longitudinal and lateral $\langle R_{11}(\boldsymbol{\xi})\rangle$
    coefficient at $z$=20m for all ABL stability cases.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
